---
title: "User_Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{User_Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = "hide"
)
```

```{r setup}
library(GLMMs)
library(dplyr)
library(tidyverse)
library(lme4)
library(broom.mixed)
```

To illustrate how to use this package to analysis data, we choose to use the dataset `epilepsy.csv` for demonstration. This dataset consists of clinical trial records of 59 patients. Each subject was initially monitored for an 8 week baseline period and the number of seizures they had was recorded. Patients were then randomized to one of two treatments, drug (31 patients) or placebo (28 patients), and the number of seizures they had was then counted over the following 8 weeks (recorded as 4 separate two week periods). We will build a Poisson model to explore whether the number of seizures a patient experiences will reduce after using the drug, after accounting for age. This is a repeat measurement experiment with 59 subjects and 2 measurements per subject.

To begin with, here are some explanatory data analysis of the dataset we used:

```{r}
epilepsy <- readr::read_csv("epilepsy.csv")

epilepsy %>%
  mutate(treatment = ifelse(treat == 0, "Placebo", "Drug"), 
         period = ifelse(expind == 0, "before", "after")) %>%
  group_by(treatment, period) %>%
  mutate(seizures = mean(seizures)) %>%
  ggplot(aes(x = treatment, y = seizures, fill = period)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  ggtitle("Average number of seizures before and after treatment")
```

```{r}
epilepsy %>%
  group_by(id) %>%
  mutate(seizures = sum(seizures), 
         treatment = ifelse(treat == 0, "Placebo", "Drug")) %>%
  ggplot(aes(x = age, y = seizures, color = treatment)) +
  geom_point() +
  ggtitle("Relation between number of seizures and age")
```

We can observe that although both the drug and placebo groups have reduction in the average number of seizures after treatment, the drug group experienced more reduction than the placebo group. Moreover, when accounted for age, those who used the drug have less total number of seizures.

Next, the code below shows how to use the `bootstrap` and `BootSummary` functions to conduct bootstrap and obtain the summary:

```{r}
## Example:

epilepsy <- epilepsy %>%
  group_by(id, treat, expind, age) %>%
  summarize(seizures = sum(seizures),
            .groups = "drop")

full_fit <- run_model(epilepsy,example = "epilepsy")
true_beta <- full_fit$beta
true_sigmasq <- full_fit$sigmasq

## Bootstrap process:
boot <- bootstrap(epilepsy, subject_index = 1, B = 100, true_beta, true_sigmasq)
## Summary of bootstrap:
BS_summary <- BootSummary(boot)

```

Variable `boot` is a 500 by 8 dataframe consisting of the summary of the bootstrap, in which each row contains the estimators, standard errors, statistic, and p value for each bootstrap iteration. The column `term` indicates which covariate the coefficient corresponds to, `estimate` is the value of estimator. The first 100 rows are the bootstrap outputs for $\beta_0$ (i.e. the intercept), and so on.

```{r}
head(boot %>% select(-group))
```

The panel of plots shown below are the densities of the bootstrap estimators:

```{r}
boot %>%
  ggplot(aes(x = estimate)) +
  geom_density() +
  facet_wrap(~term) +
  ggtitle("Distribution of bootstrap estimators")
```

Finally, below is the process of hypothesis test that whether the coefficient $\beta_4$ of the interaction term is equal to 0. Compute the proportion of time that we obtain test statistic larger(more extreme) then the t value obtained from original model fit, full_fit. We use this proportion as the p-value of the significance test.

```{r}
## hypothesis test
h0_beta <- true_beta
h0_beta[4] <- 0
boot_h0 <- bootstrap(dataset = epilepsy, h0_beta, true_sigmasq)

t_value <- full_fit$test_stat[4]
p_value <- (boot_h0 %>%
  filter(term == "expind:treat") %>%
  summarize(p = mean(abs(statistic) > abs(t_value))))$p

if(p_value < 0.05){
  print('Given 5% significance level, p value < 0.05 shows enough evidence against the null hypothesis.
        We reject H0, and beta is significantly different from 0')
} else{
  print('Given 5% significance level, p value > 0.05 does not show enough evidence against the null hypothesis.
        We do not reject H0, and beta is not significantly different from 0')
  }

```
