---
title: "User_Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{User_Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(GLMMs)
```


To illustrate how to use this package to analysis data, we choose to use the dataset `epilepsy.csv` for demonstration. This dataset consists of clinical trial records of 59 patients. Each subject was initially monitored for an 8 week baseline period and the number of seizures they had was recorded. Patients were then randomized to one of two treatments, drug (31 patients) or placebo (28 patients), and the number of seizures they had was then counted over the following 8 weeks (recorded as 4 separate two week periods). We will build a Poisson model to explore whether the number of seizures a patient experiences will reduce after using the drug, after accounting for age. This is a repeat measurement experiment with 59 subjects and 2 measurements per subject. 


```{r}
## Example:

epilepsy <- read_csv("epilepsy.csv")
epilepsy <- epilepsy %>%
  group_by(id, treat, expind, age) %>%
  summarize(seizures = sum(seizures),
            .groups = "drop")

full_fit <- run_model(epilepsy,example = "epilepsy")
true_beta <- full_fit$beta
true_sigmasq <- full_fit$sigmasq

## Bootstrap process:
boot <- bootstrap(epilepsy, subject_index = 1, B = 100, true_beta, true_sigmasq)
## Summary of bootstrap:
BS_summary <- BootSummary(boot)

```



Below is the process of hypothesis test that whether the coefficient $\beta$ is equal to 0: 

```{r}
## hypothesis test
if(0>BS_summary[4,]$LowerCI & 0<BS_summary[4,]$UpperCI){
  print('0 is inside the 95% Confidence Interval, so we do not reject H0, and beta is not significantly different from 0')
} else{
  print('0 is outside the 95% Confidence Interval, so we reject H0, and beta is significantly different from 0')
}
```



